MiP4

### 2018-05-22 MiP4.Rmd
Difference in difference modeling. Don't know what happened when I hit "stage all."

```{r setup, include=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE, cache = TRUE, message=FALSE, warning=FALSE)
library(haven) # import .dta
library(tidyverse) # everything 
library(plm) # For linear panel regression
```

```{r data import, include=FALSE}
# Alt and Lassen's "Enforcement and Public Corruption: Evidence from US States"
# http://epstein.wustl.edu/research/LPE.Alt.pdf
AltLassen <- read_dta("data/Replication/AltLassenJLEO.dta")

@@

```{r data wrangling}
# Combining Barber and ICS 
corruption <- full_join(convictions, reflections)
corruption <- corruption %>% 
  rename("st"="State", "year"="Year")
corruption$st <- state.abb[match(corruption$st,state.name)]
BarberICC <- left_join(Barber, corruption)

@@

```{r modeling, echo=FALSE}
#Next: Panel model of corruption against unemployment and high school? 
testmodel01 <- plm(CCI ~ rpcinc_annual_new + unemp + high_school + logNumpop + citi6006 + grelimp, data = AltBarber, index = c("st","year"), effect="twoways")
summary(testmodel01)

@@

>>>>

```{r setup}
knitr::opts_chunk$set(echo = TRUE, cache = TRUE, message=FALSE, warning=FALSE)
library(haven) # import .dta
library(tidyverse) # everything 
library(plm) # For linear panel regression
```

```{r data import}
# Alt and Lassen's "Enforcement and Public Corruption: Evidence from US States"
# http://epstein.wustl.edu/research/LPE.Alt.pdf
AltLassen <- read_dta("data/Replication/AltLassenJLEO.dta")

@@

```{r panel data wrangling}
# Combining Barber and ICS 
corruption <- full_join(convictions, reflections)
corruption <- corruption %>% 
  rename("st"="State", "year"="Year")
corruption$st <- state.abb[match(corruption$st,state.name)]
BarberICC <- left_join(Barber, corruption)

@@

```{r panel modeling}
#Next: Panel model of corruption against unemployment and high school? 
testmodel01 <- plm(CCI ~ rpcinc_annual_new + unemp + high_school + logNumpop + citi6006 + grelimp, data = AltBarber, index = c("st","year"), effect="twoways")
summary(testmodel01)

@@

```{r DiD wrangling}
BarberICC %>% arrange(year) %>% group_by(st) %>% mutate(
  ind_d = (ind_limits_2010 - dplyr::lag(ind_limits_2010)),
  ind_dummy_d = (ind_limits_dummy - dplyr::lag(ind_limits_dummy)),
  pac_d = (pac_limits_2010 - dplyr::lag(pac_limits_2010)),
  pac_dummy_d = (pac_limits_dummy - dplyr::lag(pac_limits_dummy)),
  ind2pty_d = (ind2pty_limits_2010 - dplyr::lag(ind2pty_limits_2010)),
  ind2pty_dummy_d = (ind2pty_limits_dummy - dplyr::lag(ind2pty_limits_dummy))
  ) -> testframe

testframe %>% select(1:2,8,11,3:7,12:21) -> DiDsmall 
summary(DiDsmall)

# Now I have what I think are three multi-level categorical independent variables. 
# https://stats.idre.ucla.edu/r/modules/coding-for-categorical-variables-in-regression-models/
#1. When limits were imposed (1) or went down, did corruption go down? 
#2. When limits were removed (-1) or went up, did corruption go up?

DiDsmall$ind_dummy_f <- factor(DiDsmall$ind_dummy_d)
DiDsmall <- within(DiDsmall, ind_dummy_f <- relevel(ind_dummy_f, ref = "0"))
DiDsmall$pac_dummy_f <- factor(DiDsmall$pac_dummy_d)
DiDsmall <- within(DiDsmall, pac_dummy_f <- relevel(pac_dummy_f, ref = "0"))
DiDsmall$ind2pty_dummy_f <- factor(DiDsmall$ind2pty_dummy_d)
DiDsmall <- within(DiDsmall, ind2pty_dummy_f <- relevel(ind2pty_dummy_f, ref = "0"))
```

```{r DiD modeling}
summary(lm(CCI ~ ind_dummy_f, data = DiDsmall))
summary(lm(CCI ~ pac_dummy_f, data = DiDsmall))
summary(lm(CCI ~ ind2pty_dummy_f, data = DiDsmall))
summary(lm(CRI ~ ind_dummy_f, data = DiDsmall))
summary(lm(CRI ~ pac_dummy_f, data = DiDsmall))
summary(lm(CRI ~ ind2pty_dummy_f, data = DiDsmall))
# No effects

summary(lm(CCI ~ ind_dummy_f*ind_d, data = DiDsmall))
summary(lm(CCI ~ pac_dummy_f*pac_d, data = DiDsmall))
summary(lm(CCI ~ ind2pty_dummy_f*ind2pty_d, data = DiDsmall))
summary(lm(CRI ~ ind_dummy_f*ind_d, data = DiDsmall))
summary(lm(CRI ~ pac_dummy_f*pac_d, data = DiDsmall))
summary(lm(CRI ~ ind2pty_dummy_f*ind2pty_d, data = DiDsmall))
# No effects

# Next: Lag, write up. 
```
